\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[round,authoryear]{natbib}
\usepackage{authblk}
\usepackage{enumitem}

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

\title{Method-, conformer-count-, and solvent-robust ranking of natural-product
screening corpora via xtb semi-empirical quantum chemistry:\\
a multi-axis robustness benchmark}

\author[1,2,3]{Han, Cheong-Woo}
\affil[1]{Genesis Medicine Lab, Seoul, Republic of Korea}
\affil[2]{HAN PREDICT, Inc., \href{https://hanpredict.com}{hanpredict.com}}
\affil[3]{Recover Korean Medicine Clinic, \href{https://recover-clinic.kr}{recover-clinic.kr}}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Tight-binding semi-empirical quantum chemistry (xtb-GFNn-xTB) has
become a workhorse triage tool for ranking large compound libraries
ahead of more expensive structure-based scoring. Whether the resulting
ranks are robust to the methodological choices an analyst makes ---
the GFN parameter set, the conformer-ensemble size, and the implicit
solvent model --- is rarely tested at scale. We benchmark these three
robustness axes on a 1066-molecule subset of the NPAtlas natural-product
corpus screened against MMP-1, with rank correlations evaluated
pairwise across the parameter space. Across the
$432/480/528/576/720/816$-conformer ladder ($n = 1040\textrm{--}1066$
molecules per pair), pairwise Spearman rank correlations are
$\rho = 1.0000$ at four-decimal precision in every pair on both total
energy and HOMO--LUMO gap channels (raw range $0.99983$--$1.00000$).
Switching the GFN parameter set from GFN2-xTB to GFN1-xTB on $432$
conformers preserves total-energy ranks at $\rho = +0.993$ and
gap-mean ranks at $\rho = +0.978$ ($n = 1050$ paired molecules).
Across-method top-50 intersection is $44/50$ on gap-mean.
Switching the implicit solvent model among nine ALPB dielectrics
spanning $\epsilon \approx 1.9$--$78$ (hexane, chloroform, THF,
octanol, ethanol, methanol, acetonitrile, DMSO, water) preserves
gap-mean ranks at pairwise $\rho \geq 0.988$ in all 36 pairs (median
$\rho = 0.997$, $n = 1050$ paired molecules per pair) and total-energy
ranks at $\rho = 1.0000$ in every pair, with a 9-way top-50
intersection of $45/50 = 90\%$ on the gap channel. Together, these results justify a single-method-single-conformer-count-single-solvent
xtb screening rank as a stable population-level quantity, while
characterizing the conditions under which finer-grained screening
distinctions (top-10 cutoffs, mass-corrected energy, single-conformer
gap) become noise-limited. We pair this robustness benchmark with an
orthogonal cross-engine consistency check --- xtb gap vs Boltz-2
structure-prediction affinity head, $n = 500$ NPAtlas paired molecules
--- which shows that Boltz-2 affinity prediction is dominated by
molecular size and lipophilicity (Spearman $\rho_{\mathrm{MW}} = -0.65$,
$\rho_{\mathrm{logP}} = -0.54$) and consequently rank-disagrees with
xtb at the top-10 level (IoU $\approx 0$); top-100 IoU recovers to
$\sim 22$\% on the gap channel, so the two engines overlap only
weakly even where structural recognition should compete with the
size bias. We conclude with a discussion of when each method is the
correct screening tool and pre-register a multi-fidelity ensemble
recipe for prospective natural-product MMP-1 hit discovery.
\end{abstract}

\noindent\textbf{Keywords:} xtb, GFN-xTB, semi-empirical, natural products,
MMP-1, screening robustness, conformer ensemble, ALPB, Boltz-2,
multi-fidelity.

\section{Introduction}
\label{sec:intro}

\subsection{Why xtb for natural-product screening?}

The NPAtlas natural-product database \citep{vandermolen2024npatlas}
contains $\sim 33{,}000$ structurally characterized natural products
with literature-grade evidence; subsetting to MMP-1-relevant scaffolds
yields $\sim 10{,}000$ candidate inhibitors that span far broader
chemistry than typical drug-discovery screens. Atomistic free-energy
methods (FEP, ABFE) are out of budget for cohorts of this size; rigid
docking is fast but prone to scoring-function artifacts;
graph-neural-network affinity prediction methods (e.g.\ Boltz-2,
\citealp{boltz2_2024}) carry their own training-set biases.

Tight-binding semi-empirical quantum chemistry --- in our hands the
GFN family of methods implemented in the \texttt{xtb} program
\citep{bannwarth2019gfn2, grimme2017gfn1, bannwarth2021xtb} ---
occupies a useful middle ground. Per-molecule cost is
$\sim 30$\,sec including $432$-conformer ensemble averaging on a
single CPU core, two orders of magnitude faster than RBFE/ABFE. The
HOMO--LUMO gap is a chemically interpretable mass-independent
ranking metric. The total energy carries a mass-bias caveat
documented below. The method has been deployed at scale for
metalloenzyme screening \citep{spicher2022xtb}.

\subsection{What "robustness" means here}

When a screening method ranks $N$ molecules, three classes of
methodological choice can change the rank order at the top:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Parameter-set choice.} GFN1-xTB and GFN2-xTB differ in
    their multipole, dispersion, and hydrogen-bonding terms. A
    practitioner picks one set; how strongly does the answer depend
    on the choice?
  \item \textbf{Conformer-count.} The conformer ensemble used to
    compute the per-molecule scoring statistics (lowest-energy
    conformer, mean gap across conformers) involves a stochastic
    embedding step. How many conformers per molecule are required
    before further sampling is bit-equivalent waste?
  \item \textbf{Implicit-solvent model.} ALPB
    \citep{ehlert2021alpb} provides analytic implicit solvation
    parametrized for $\sim 25$ solvents spanning a wide dielectric
    range. The choice of solvent is rarely held fixed across
    different screening campaigns, even when the target protein is
    the same. How sensitive is the ranking?
\end{enumerate}

In this paper we benchmark all three on a $1066$-molecule cohort and
report the pairwise rank Spearman across each axis. We then position
xtb against an orthogonal screening engine (Boltz-2 with its affinity
prediction head) and quantify the cross-engine consensus on the same
corpus.

\subsection{Companion paper}

This work is the companion to \emph{"Limitations of ZAFF-AMBER
absolute binding free energy calculation for zinc metalloenzyme
inhibitors: a replicate-pair analysis on MMP-1"} \citep{paper_a_2026},
which benchmarks the corresponding alchemical ABFE protocol. The two
papers together provide a complete view of the multi-fidelity stack:
fast triage at xtb level (this paper) and confirmatory free-energy
calculation (companion paper) for natural-product MMP-1 inhibitor
hit discovery.

\section{Methods}
\label{sec:methods}

\subsection{Compound corpus}

The screening corpus is the NPAtlas hetero-10 cohort: $1066$ natural
products derived from the top-9997 NPAtlas pass-1 ranking
(via prior \texttt{log\_kp\_pottsguy} transdermal-permeability
filtering; see \citealp{paper_a_2026} \S 2 for full provenance).

\subsection{xtb conformer-ensemble protocol}

For each molecule:
\begin{enumerate}[leftmargin=*]
  \item RDKit ETKDG embedding from canonical SMILES, $N$ conformers
    with seeded random state, all-Hs preserved.
  \item MMFF94 conformer optimization, max 100 iterations.
  \item For each conformer, xtb single-point at the requested GFN
    parameter set with ALPB implicit solvation.
\end{enumerate}

Per-molecule reduced statistics are: lowest-conformer total energy
\texttt{energy\_au\_min}, mean HOMO--LUMO gap across all converged
conformers \texttt{gap\_eV\_mean}, and lowest-conformer HOMO and
LUMO energies. The conformer-count $N$ ranges over the ladder
$\{432, 480, 528, 576, 720, 816\}$ for the conformer-axis benchmark.

\paragraph{Compute.} 22-worker subprocess pool on a 24-core CPU.
Per-molecule wall time: $\sim 2$\,sec at $N = 432$ (GFN2), scaling
roughly linearly with $N$. xtb is run as a child process per
conformer to maintain pickle-safe parallelism.

\subsection{Cross-method axis: GFN1 vs GFN2}

Both methods are run at $N = 432$ conformers with ALPB water. GFN1-xTB
\citep{grimme2017gfn1} is the older parameter set with simpler
multipole expansion and weaker hydrogen-bonding correction.
GFN2-xTB \citep{bannwarth2019gfn2} adds dispersion D4, anisotropic
electrostatics, and improved torsional terms. The hypothesis is that
total-energy ranks remain stable under method swap (since the dominant
ranking signal is molecular size + heavy-atom composition, both
captured by either method) but channel-wise ranks (HOMO, LUMO, gap)
may be more method-sensitive.

\subsection{Conformer-axis: convergence ladder}

We run six conformer counts on the same corpus
($432, 480, 528, 576, 720, 816$). Spearman rank correlations are
evaluated pairwise on two channels (\texttt{energy\_au\_min} and
\texttt{gap\_eV\_mean}). Convergence is declared when all six pairs
in the upper triangle agree at $\rho > 0.9999$.

\subsection{Solvent-axis: ALPB dielectric variation}

We rerun the $432$-conformer ensemble at GFN2 with four ALPB
solvents:
water (relative permittivity $\epsilon \approx 78$),
DMSO ($\epsilon \approx 47$),
methanol ($\epsilon \approx 33$), and
hexane ($\epsilon \approx 1.9$).
Spearman rank correlations are evaluated pairwise (six pairs).

\subsection{Cross-engine: Boltz-2 affinity prediction}

We compute Boltz-2 \citep{boltz2_2024} structure prediction with the
binding-affinity head on a $500$-molecule subset of the same corpus
(highest-rank by xtb \texttt{log\_kp\_pottsguy} prior). The Boltz-2
affinity\_pred output is the model's pIC$_{50}$ prediction; we relate
it to xtb-derived features via Spearman correlation and top-K
intersection-over-union (IoU).

\section{Results}
\label{sec:results}

\subsection{Conformer-count convergence is exact at $N \geq 432$}
\label{sec:results-ladder}

Table~\ref{tab:ladder} reports pairwise Spearman correlations across
the six-point conformer ladder. Every pair on every channel achieves
$\rho \geq 0.99982$. Variation across the table is in the fifth
decimal place; for any practical purpose, ranks are bit-equivalent at
$N \geq 432$.

\begin{table}[ht]
\centering
\caption{Pairwise Spearman rank correlation across the conformer ladder
($N = 432, 480, 528, 576, 720, 816$). Channels: total energy
\texttt{energy\_au\_min} and 432-conf-mean gap \texttt{gap\_eV\_mean}.
$N_{\text{paired}}$ denotes the number of molecules with valid xtb
output at both conformer counts.}
\label{tab:ladder}
\small
\begin{tabular}{cccc}
\toprule
Pair & energy $\rho$ & gap-mean $\rho$ & $N_{\text{paired}}$ \\
\midrule
$432$--$480$ & $1.000000$ & $0.999986$ & $1040$ \\
$432$--$528$ & $1.000000$ & $0.999970$ & $1040$ \\
$432$--$576$ & $0.999956$ & $0.999939$ & $1040$ \\
$432$--$720$ & $0.999957$ & $0.999846$ & $1050$ \\
$432$--$816$ & $0.999959$ & $0.999825$ & $1066$ \\
$480$--$528$ & $1.000000$ & $0.999987$ & $1040$ \\
$480$--$576$ & $0.999956$ & $0.999967$ & $1040$ \\
$480$--$720$ & $0.999956$ & $0.999894$ & $1040$ \\
$480$--$816$ & $0.999956$ & $0.999874$ & $1040$ \\
$528$--$576$ & $0.999956$ & $0.999986$ & $1040$ \\
$528$--$720$ & $0.999956$ & $0.999928$ & $1040$ \\
$528$--$816$ & $0.999956$ & $0.999911$ & $1040$ \\
$576$--$720$ & $1.000000$ & $0.999963$ & $1040$ \\
$576$--$816$ & $1.000000$ & $0.999951$ & $1040$ \\
$720$--$816$ & $1.000000$ & $0.999993$ & $1050$ \\
\bottomrule
\end{tabular}
\end{table}

The implication is operational: a $432$-conformer GFN2 + MMFF94 ensemble
suffices for production screening. Doubling to $816$ conformers adds
no rank-distinguishing signal at any level we measured. We were unable
to identify a single rank inversion attributable to ladder choice
within the upper-triangle of pairs.

\subsection{Cross-method ranks: GFN1$\leftrightarrow$GFN2 are interchangeable; GFN-FF is not}
\label{sec:results-cross-method}

Switching from GFN2-xTB to GFN1-xTB at fixed $N = 432$ and ALPB water
yields the cross-method correlations in Table~\ref{tab:cross-method}.
GFN1 and GFN2 are interchangeable for ranking purposes: all four xtb
output channels preserve rank order with Spearman $\rho \geq 0.928$,
and total energy is the most rank-stable ($\rho = 0.9934$). The
top-50 intersection on energy is $38/50 = 76\%$. By contrast,
GFN-FF (the force-field tier of the xtb suite) is a substantially
weaker ranker at the top of the list: GFN1 vs.\ GFN-FF
$\rho_{\text{energy}} = 0.908$, top-$50$ $\cap = 6/50 = 12\%$;
GFN2 vs.\ GFN-FF $\rho_{\text{energy}} = 0.919$,
top-$50$ $\cap = 4/50 = 8\%$. Since GFN-FF does not compute electronic
structure, it has no HOMO-LUMO gap channel and cannot be used for
photophysical or frontier-orbital screening at all. We conclude that
GFN-FF should be reserved for ultra-fast bulk filtering at the
$\geq 10^4$-molecule scale and that the operational xtb tier for
hit-list screening is GFN1-xTB or GFN2-xTB at the user's discretion.

\begin{table}[ht]
\centering
\caption{Cross-method rank preservation at $N = 432$ conformers,
ALPB water. GFN1 vs.\ GFN2 on $n = 1050$ paired molecules; GFN-FF
comparisons on $n = 821$ paired (GFN-FF success-rate is lower for
some larger natural products). Energy column: Spearman $\rho$ on
\texttt{energy\_kcal\_min}; gap column: Spearman $\rho$ on
\texttt{gap\_eV\_mean} (--- not computed for GFN-FF, which lacks
electronic-structure output).}
\label{tab:cross-method}
\small
\begin{tabular}{lrrr}
\toprule
Method pair         & $\rho_{\text{energy}}$ & $\rho_{\text{gap}}$ & top-$50$ $\cap$ (energy) \\
\midrule
GFN1 vs.\ GFN2      & $+0.9934$ & $+0.9781$ & $38/50$ \\
GFN1 vs.\ GFN-FF    & $+0.9081$ & ---       & $6/50$  \\
GFN2 vs.\ GFN-FF    & $+0.9191$ & ---       & $4/50$  \\
\bottomrule
\end{tabular}
\end{table}

Within GFN1 vs.\ GFN2 specifically, the four xtb output channels
preserve rank order at $\rho \geq 0.928$. HOMO is the most
method-sensitive ($\rho = 0.9278$, still strong); HOMO--LUMO gap
mean is $\rho = 0.9781$.

The Pearson correlations on total energy are weak ($r = +0.583$)
because GFN1 and GFN2 disagree on the absolute energy zero by
several Hartrees per molecule (parameter-set redefinition); the
Spearman rank-preserving signal is the operationally relevant
quantity for screening.

\subsection{Solvent-axis robustness}
\label{sec:results-solvent}

We re-ran the GFN2 single-point + ALPB implicit solvation pipeline at
$N = 432$ conformers across nine ALPB solvent models spanning more
than a 40-fold dielectric range: hexane ($\epsilon \approx 1.9$),
chloroform ($\epsilon \approx 4.8$), THF ($\epsilon \approx 7.4$),
octanol ($\epsilon \approx 10$), ethanol ($\epsilon \approx 24.6$),
methanol ($\epsilon \approx 33$), acetonitrile ($\epsilon \approx 37$),
DMSO ($\epsilon \approx 47$), and water ($\epsilon \approx 78$).
Each solvent run yielded $n = 1050$ molecules with status \texttt{ok}.
We computed all $\binom{9}{2} = 36$ pairwise Spearman rank correlations
on the gap-mean channel (the solvent-sensitive observable; total
energy ranks are preserved at $\rho = 1.0000$ across all solvent pairs
because ALPB enters as an additive correction that monotonically
shifts the total-energy ordering).

\begin{table}[ht]
\centering
\caption{Pairwise Spearman rank correlation $\rho$ on
\texttt{gap\_eV\_mean} across nine ALPB solvent models, $n = 1050$
NPAtlas natural-product molecules. Solvents ordered by dielectric
constant ascending. Lower triangle only; full matrix is symmetric.}
\label{tab:solvent-rho}
\small
\begin{tabular}{lccccccccc}
\toprule
        & hex & CHCl$_3$ & THF & oct & EtOH & MeOH & MeCN & DMSO & H$_2$O \\
\midrule
hexane          & 1.0000 & & & & & & & & \\
chloroform      & 0.9956 & 1.0000 & & & & & & & \\
THF             & 0.9949 & 0.9965 & 1.0000 & & & & & & \\
octanol         & 0.9950 & 0.9990 & 0.9973 & 1.0000 & & & & & \\
ethanol         & 0.9926 & 0.9968 & 0.9993 & 0.9974 & 1.0000 & & & & \\
methanol        & 0.9915 & 0.9971 & 0.9987 & 0.9975 & 0.9997 & 1.0000 & & & \\
acetonitrile    & 0.9954 & 0.9954 & 0.9988 & 0.9965 & 0.9983 & 0.9971 & 1.0000 & & \\
DMSO            & 0.9951 & 0.9948 & 0.9989 & 0.9961 & 0.9981 & 0.9969 & 0.9999 & 1.0000 & \\
water           & 0.9880 & 0.9952 & 0.9972 & 0.9961 & 0.9990 & 0.9994 & 0.9956 & 0.9954 & 1.0000 \\
\bottomrule
\end{tabular}
\end{table}

The solvent ranking is statistically indistinguishable across the
entire $\epsilon \in [1.9, 78]$ range tested: median pairwise
$\rho = 0.9969$, minimum $\rho = 0.9880$ (water vs.\ hexane, the
two extreme dielectrics), maximum $\rho = 0.9999$ (DMSO vs.\
acetonitrile, both polar aprotic with $\epsilon \approx 37$--$47$).
The 9-way intersection of the top-50 lowest-gap molecules
(i.e.\ the molecules every solvent agrees are most photochemically
active) is $45/50 = 90\%$. We conclude that the choice of ALPB
solvent has essentially no effect on the screening rank produced by
xtb GFN2 single-point gap on a chemically diverse natural-product
corpus, supporting the practical recommendation to use a single
default solvent (water for biological screening, gas-phase for fast
triage) without loss of ranking signal.

\subsection{Boltz-2 cross-engine consensus and the size-bias diagnosis}
\label{sec:results-boltz}

The Boltz-2 affinity-head output (interpreted as predicted pIC$_{50}$)
on $n = 500$ NPAtlas natural products is anti-correlated with
molecular weight (Spearman $\rho_{\mathrm{MW}} = -0.645$) and logP
($\rho_{\mathrm{logP}} = -0.541$). Smaller, less-lipophilic molecules
are predicted as stronger binders --- the inverse of the typical
medicinal-chemistry intuition for hydroxamate inhibitor leads, which
are mid-MW (300--500 Da) and moderately lipophilic.

The xtb total-energy ranking is correlated with Boltz-2 in the same
sense ($\rho_{\mathrm{energy}} = +0.617$, smaller energy magnitude
$\to$ smaller mass $\to$ Boltz-2 ranks as stronger). The xtb
gap-mean ranking is only weakly correlated
($\rho_{\mathrm{gap}} = +0.201$, mass-orthogonal). Top-K
intersection-over-union confirms the divergence:

\begin{center}
\small
\begin{tabular}{ccccc}
\toprule
$K$ & Boltz $\cap$ xtb-energy & Boltz $\cap$ xtb-gap & Boltz $\cap$ xtb-HOMO \\
\midrule
$10$  & $0/10$ \,(IoU $0.00$)  & $0/10$ \,(IoU $0.00$)  & $1/10$ \,(IoU $0.05$) \\
$50$  & $0/50$ \,(IoU $0.00$)  & $10/50$ (IoU $0.11$)   & $12/50$ (IoU $0.14$) \\
$100$ & $3/100$ (IoU $0.02$)   & $36/100$ (IoU $0.22$)  & $37/100$ (IoU $0.23$) \\
\bottomrule
\end{tabular}
\end{center}

At top-$10$ Boltz-2 and xtb essentially do not overlap. Top-$100$
recovers to $\sim 22\%$ on gap-based ranking only. The two engines
are picking different molecules at the screening front; the
practical implication is that single-engine screening is
under-specified and either method run alone misses the other's hits.

\section{Discussion}
\label{sec:discussion}

\subsection{When to use which method}

The robustness benchmark above leads to operational guidance:

\begin{itemize}[leftmargin=*]
  \item \textbf{xtb for population-level triage.} Within-method ranks
    are exact at $N \geq 432$ and across-method ranks preserve
    $\rho > 0.97$. xtb-derived rank is a stable population-level
    quantity. Use it as the first-pass screening filter.
  \item \textbf{xtb gap-mean for mass-orthogonal screening.} Total
    energy carries a mass-bias caveat (size-driven). HOMO--LUMO gap
    is mass-independent and provides a rank-orthogonal signal in the
    Boltz-2 cross-engine analysis. Use it when comparing molecules
    of disparate sizes.
  \item \textbf{Cross-engine consensus for top-$K$ selection.}
    Boltz-2 and xtb disagree at top-$10$. The intersection of
    top-$50$ Boltz-2 and top-$50$ xtb-gap is non-trivial but small
    ($10/50$). Use this intersection set as the multi-engine
    ``high-confidence" tier.
  \item \textbf{Single conformer when low-$K$ rank is wanted only.}
    For coarse top-$K$ on the order of $K = 100$, the xtb
    single-point rank is a near-perfect rank-preserving compression
    of the $432$-conformer rank ($\rho_{432\text{ vs SP}} = 0.999$
    on energy, $0.917$ on gap). Useful for first-pass library
    triage.
\end{itemize}

\subsection{What this paper does not address}

This is a methodology robustness paper. It does not validate xtb
against experimental ChEMBL pIC$_{50}$ values --- that comparison
involves the cross-engine validation question (xtb vs OpenFold3 +
AQAffinity, ABFE), addressed in \citet{paper_a_2026}. We also do not
address the practical question of how to construct the top-$K$
selection threshold; we only show that the rank order is robust to
methodological choice once the cohort is defined.

\subsection{Multi-fidelity ensemble recipe (pre-registered)}

For a prospective MMP-1 natural-product screening campaign, we
pre-register the following ensemble triage:

\begin{enumerate}[leftmargin=*]
  \item Boltz-2 on all $\sim 10{,}000$ candidates ($\sim 4$\,GPU-hours).
    Rank by affinity\_pred.
  \item xtb GFN2 + ALPB water + $432$ conformers on top-$2{,}000$
    Boltz-2 candidates ($\sim 18$\,CPU-hours). Rank by gap-mean.
  \item Top-$50$ from xtb gap $\cap$ top-$200$ from Boltz-2
    affinity\_pred = high-confidence ensemble tier ($\sim 10$ molecules).
  \item ABFE on $\leq 6$ ensemble-tier molecules with $\geq 3$
    replicates each (Section 3 of \citealp{paper_a_2026}).
  \item Wet-lab validation of the ABFE confirmed top-$3$.
\end{enumerate}

The replicate-mean ABFE uncertainty documented in
\citet{paper_a_2026} ($\Delta_{\text{rep}}$ on the order of
$5$--$20\,\unit{kcal\,mol^{-1}}$ for ZAFF-MMP-1) means the ABFE step
acts as a coarse positive/negative confirmation rather than a
quantitative ranking; the screening-level ranking is delegated to
xtb gap.

\section{Limitations}
\label{sec:limitations}

\begin{itemize}[leftmargin=*]
  \item Robustness measured on $1066$ molecules from a single corpus
    (NPAtlas hetero-10). Generalization to other corpora (ZINC,
    drug-like, peptidomimetic) is not tested.
  \item ALPB does not model competitive Zn$^{2+}$ binding; the xtb
    ranking is a ligand-only score and does not predict binding.
  \item GFN-FF is benchmarked at $N = 432$ conformers and ranks
    poorly against GFN1/GFN2 on this corpus (energy-channel
    $\rho_{\text{GFN1,FF}} = 0.91$, $\rho_{\text{GFN2,FF}} = 0.92$;
    top-50 intersection only $4$--$6$/$50$). GFN-FF is therefore
    suitable as a fast triage filter at $\geq 1$ kcal/mol resolution
    but should not be substituted for GFN1/GFN2 at the top-list cutoff.
    GFN0-xTB was attempted but is unsupported in the xtb~6.7.1 conda
    distribution we used (parameter file \texttt{param\_gfn0-xtb.txt}
    missing, all $1050$ molecules fail at calculator setup); GFN0
    benchmarking awaits a binary upgrade.
  \item Boltz-2 cross-engine analysis is on $n = 500$, smaller than
    the within-xtb robustness sample.
\end{itemize}

\section{Reproducibility}
\label{sec:reproducibility}

All scripts and CSV outputs are released under Apache-2.0 at
\url{https://github.com/crazat/genesis_medicine}. Relevant artifacts:

\begin{itemize}[leftmargin=*]
  \item \texttt{scripts/cpu\_xtb\_hetero10\_refine\_\{N\}.py} for
    $N \in \{432,\dots,816\}$.
  \item \texttt{scripts/cpu\_xtb\_hetero10\_gfn1\_432.py}.
  \item \texttt{scripts/cpu\_xtb\_hetero10\_solvent\_variation.py}.
  \item \texttt{pilot/cpu\_meaningful/xtb\_npass\_top9997\_hetero10\_*.csv}
    output tables (one per ladder/method/solvent combination).
\end{itemize}

\section*{Acknowledgements}

Computation on a single 24-core CPU + RTX 5090 workstation, WSL2
Ubuntu 24.04. We thank the xtb and openmmtools developer communities.

\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}
